An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-22 neurips-19/poly-embed.tex
Revisiting the top k example

%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = 1-\max_{y\in\Y} p_y$. \jessiet{Isn't that the Score $G$?  Don't we want $\risk{\ell} = 1 - \min_{y \in \Y} p_y$?}\raft{did you mean $1-\max$?}
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, the hinge loss is polyhedral, whereas logistic loss is not.

@@

Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\raft{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate or general properties.
% Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
% In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.

@@

\subsection{Links and Embeddings}

To ensure consistency, we will seek ``calibration''  of the surrogate and link function.
\raft{Separated stuff commented out}
% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.

% \begin{definition}[Consistency]\label{def:consistency}
%   A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
% \end{definition}

% \begin{definition}[Separated Link]\label{def:links}
%   Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
%   A \emph{link function} is a map $\psi:\reals^d\to\R$.
%   We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
%   \begin{align*}
%     \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
%   \end{align*}
%   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
% \end{definition}

\begin{definition}
    \[ \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)} . \]
\end{definition}

Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss and has the same statistical behavior.
We formalize this notion as follows.
%
\begin{definition}\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
\end{definition}
%

Note that it is not clear if embeddings give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know... just wanted to say that} via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
Constructing separated links from embeddings will therefore be a major focus in Section~\ref{sec:poly-loss-embed}.

@@

We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $|\Y|$.

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\citet[Corollary 13.3.1]{rockafellar1997convex}.
  Note that $-\risk{\ell}$ is a closed convex function, as the infimum of affine functions, and thus $(-\risk{\ell})^{**} = -\risk{\ell}$.
  Define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
  We first show that $L$ embeds $\ell$, and then establish that the range of $L$ is in fact $\reals^\Y_+$, as desired.

  We compute Bayes risks and apply Proposition~\ref{prop:embed-bayes-risks} to see that $L$ embeds $\ell$.
  For any $p\in\simplex$, we have
  \begin{align*}
    \risk{L}(p)
    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}
    \\
    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}
    \\
    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)
    \\
    &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
  \end{align*}
  It remains to show $L(u)_y \geq 0$ for all $u\in\reals^n$, $y\in\Y$.
  Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
  \raft{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.  (Not needed for NeurIPS since we don't focus on the dimension.)}
\end{proof}

@@

Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of polyhedral surrogates for the top-$k$ classification problem.
Using our embedding framework, we show how to simplify their arguments.

The top $k$ classification problem takes as input a vector $r \in \R = \{r \in \{0,1\}^n : |r| = k\}$, \raf{mixing sets and indicators here, unless you mean $\|r\|_1$} and observes outcome $y \in \{1,2,\ldots, n\}$.

We say the top-$k$ loss $\ell_{top-k}:\R \to \reals$ is
\begin{align}
\ell_{top-k}(r,y) = \begin{cases}
0 & r_y = 1\\
1 & \text{otherwise}
\end{cases}
\end{align}

Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
Additionally, Yang and Koyejo evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but its consistency is left as an open question.

After our discussion of embeddings, we now have a way of proving inconsistency: if a surrogate $L$ embeds a discrete loss $\ell$, then $L$ is consistent with respect $\ell$. \jessie{I suppose we still need a proof of this.}
Moreover, if for some other discrete loss $\ell' \neq \ell$,
\raf{Consistency: it's is about the expected loss over $(x,y)$ pairs, and showing that getting the best surrogate loss should mean getting the best original loss.  Take another look at Theorem 2.4 of the top-k paper.  Losses can certainly be consistent without embedding $\ell$ (even if polyhedral: you can link multiple embedded points to a single discrete report, e.g.\ a convex surrogate for ranking loss can link to the mode), so the ``iff'' is not right.  I think it's worth spending some time thinking about what exactly we need to show to prove inconsistency.  In particular, see if this reasoning checks out:  Suppose we find a distribution $p$ for which an optimal surrogate report is $r$ but $\psi(r)$ is not optimal for $\ell$.  Since we could have a conditional distribution of $p$ for every $x$, so the optimal hypothesis would just be the constant function $h(x) = r$, which achieves the optimal $L$-loss, and when linked, $\psi \circ h(x) = \psi(r)$, which does not achieve the optimal $\ell$-loss.}
\jessie{I think what we want to say is the following: if $L$ embeds $\ell$, then $L$ is consistent with respect to $\ell$.  Moreover, if $\ell \neq \ell'$ and $L$ embeds $\ell$, then $L$ does not not embed $\ell'$.  Can we take this and say something about $L$ not being consistent wrt $\ell'$?}
We can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent in a more suffice manner; we do so by showing the discrete loss that their surrogate embeds is not equal to  $\ell_{top-k}$.

Here, $r \in 2^n$ can be thought of as a binary 0-1 vector representing set inclusion and $k \leq n$ is a constant.
There is some ambiguity on how $t_k(r)$ should be defined if $\|r \|_\infty > k$, so we shall say that $y \not \in t_k(r)$ in such instances.

Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
Following the numbering of Yang and Koyejo, we call the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.

It can be verified that
$\ell_2(r,y) = \begin{cases}
\min\left(\frac{HD(r, e_y)}{k}, 1\right) & r_y = 1 \\
1 + \min \left(\frac{HD(s, \vec{0})}{k}, 1\right) & r_y = 0
\end{cases}$,
 where $HD(\cdot, \cdot)$ is the Hamming distance between two vectors.

Since we can see that $\ell_2 \neq \ell_{top-k}$, we can then see that $L_2$ is not consistent with respect to $\ell_{top-k}$.
Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.

So even though the surrogates $L_2$ and $L_4$ are convex, they are not consistent with respect to $\ell_{top-k}$.
This begs the question: what is the relationship between consistency and convexity of a surrogate loss?
Are there instances where only one can be achieved, but not both?

>>>>

\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = \max_{y\in\Y} p_y$. \jessie{Isn't that the Score $G$?  Don't we want $\risk{\ell} = 1 - \min_{y \in \Y} p_y$?}
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex \jessie{and bounded from below?}; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, the hinge loss is polyhedral, whereas logistic loss is not.

\subsection{Links and Embedding}

To ensure consistency, we will seek ``separated'' link functions, which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.

\begin{definition}[Consistency]\label{def:consistency}
  A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
\end{definition}

\begin{definition}[Separated Link]\label{def:links}
  Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
  A \emph{link function} is a map $\psi:\reals^d\to\R$.
  We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
  \begin{align*}
    \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
  \end{align*}
  A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
\end{definition}

Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss and has the same statistical behavior.
We formalize this notion as follows.
%
\begin{definition}\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  \begin{equation}\label{eq:embed-loss}
    r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  \end{equation}
\end{definition}
%
Note that it is not clear if embeddings give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know... just wanted to say that} via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
Constructing separated links from embeddings will therefore be a major focus in Section~\ref{sec:poly-loss-embed}.

@@

Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the finite property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

For finite properties and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate or general properties.
Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.

@@

\begin{theorem}\label{thm:polyhedral-embed-prop}
	Every polyhedral loss embeds a finite elicitable property.
	%Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}

@@

We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $n-1$.
\raft{Should revisit this statement at the end; I have a feeling we'll want to kill ``$n$'' throughout the paper since we focus so much less on it, and the reader won't remember what $n$ is.}

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  \raf{NOTE: need to ensure nonnegativity of $L$}
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
\end{proof}

@@

Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of polyhedral surrogates for the top-$k$ classification problem.
We are also able to show inconsistency using our embedding framework.
\jessie{Add sentence on what top-k problem is intuitively.}

The top $k$ classification problem takes as input a set $r \in \R := \{r \subseteq [n] : |r| = k\}$, and observes outcome $y \in [n]$.
We define the top-$k$ loss $\ell_{top-k}:\R \to \reals$ by
\begin{align}\label{eq:top-k}
\ell_{top-k}(r,y) = \begin{cases}
0 & y \in r\\
1 & \text{otherwise}
\end{cases}
\end{align}

Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that their surrogate is not convex.
Additionally, they evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but their consistency is left as an open question.
Following the notation of Yang, we call Lapin's~\cite{lapin2018analysis} convex surrogate $L_2$, and primarily focus on this.
Here, we assume $r \subseteq [n]$ and $k \leq n$ is a constant.

Our embedding framework can help lead us to distributions where the surrogate loss is not minimized by predicting the minimizer of $\ell_{top-k}$.
First, we want to show that for all $p \in \simplex$, there (1.) is some $u \in \{0,1\}^n$ that minimizes $\inprod{p}{L_2(\cdot)}$.
Then, we show (2.) there is a discrete loss $\ell_2$ that is embedded by $L_2$, where the embedded reports are the corners of the $n$-dimensional hypercube.
For $k=1$, we know that the $\ell_{top-k}$ reduces to 0-1 loss, so finally, we (3.) characterize the distributions where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.

\raft{Take another look at Theorem 2.4 of the top-k paper.  Losses can certainly be consistent without embedding $\ell$ (even if polyhedral: you can link multiple embedded points to a single discrete report, e.g.\ a convex surrogate for ranking loss can link to the mode), so the ``iff'' is not right.  I think it's worth spending some time thinking about what exactly we need to show to prove inconsistency.  In particular, see if this reasoning checks out:  Suppose we find a distribution $p$ for which an optimal surrogate report is $r$ but $\psi(r)$ is not optimal for $\ell$.  Since we could have a conditional distribution of $p$ for every $x$, so the optimal hypothesis would just be the constant function $h(x) = r$, which achieves the optimal $L$-loss, and when linked, $\psi \circ h(x) = \psi(r)$, which does not achieve the optimal $\ell$-loss.}

Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
We write the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.

Consider the following process:  (1.) For all $p \in \simplex$, we can show that there is some $u \in \{0,1\}^n$ such that $u \in \argmin_{u'} \inprod{p}{L_2(u')}$.
(2.) Now consider the discrete loss
\begin{align*}
\ell_2(r,y) &= 1 - \Ind[y \in r] + \min\left(\frac{|r| \setminus \{y\}}{k}, 1\right)
\end{align*}
We claim that $L_2$ embeds $\ell_2$.  
(3.) Finally, taking $k = 1$, we see that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.

\begin{enumerate}
	\item \jessie{TODO-- taking a quick break.}

	\item We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{0,1\}^n$.
	Moreover, by part (1.) and the above verification, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \{0,1\}^n} \inprod{p}{L_2(u)} = \min_{r \subseteq}\ell_2(r)$, and so we conclude that $L_2$ embeds $\ell_2$.

	\item First, we see that $\ell(\vec{0}, \bar{p}) = 1$.
	Taking any basis vector $e_y$, the expected loss $\ell_2(e_y, p) = 2 (1-p_y) \geq 1$ by assumption on $p$. 
	For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r,y) \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
	Therefore, we have that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.
\end{enumerate}

Thus, we can use our embedding framework to distinguish distributions where a surrogate is not consistent with respect to a given discrete loss.

%Since we can see that $\ell_2 \neq \ell_{top-k}$, we can then see that $L_2$ is not consistent with respect to $\ell_{top-k}$.
%Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
%We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.
